---
title: "Homework1"
output: html_document
author: "Sümeyra Özuğur"
---



### 1)Import “heros_information” dataset from https://www.kaggle.com/claudiodavi/superhero-set

```{r}
#import data
mydata = read.csv("C:/Users/asus/Desktop/4.Sınıf/DataScience/sumeyra_ozugur_HW1/heroes_information.csv")  
head(mydata)

```

### 2)How many male characters that have blue eyes are there?

```{r}

library(dplyr)


blue_eyes_male <- mydata %>% 
     filter(Gender == "Male", Eye.color == "blue") %>% 
     select(Gender,Eye.color)
count(blue_eyes_male)

#for (number in blue_eyes_male){
  #print(number)
 # length(number)
#}

```

### 3) Remove bad alignment and answer Q2 again.
```{r}

    remove_bad_alignment <- mydata %>%
    filter(Alignment != "bad" & Eye.color=="blue" & Gender=="Male") 
   
count(remove_bad_alignment)



```

### 4)What is the most common race and skin color? Create a summary table
```{r}


most_common_race <- mydata %>% 
  group_by(Race) %>%
  filter(Race != "-") %>%
  summarise('Racee'=n())
arrange(most_common_race,desc(Racee))




```
According to this output the most common Race is **Human** .


```{r, message=FALSE}

most_common_skincolor <- mydata %>% 
  group_by(Skin.color) %>%
   filter(Skin.color != "-") %>%
  summarise('SkinnColor'= n())
arrange(most_common_skincolor,desc(SkinnColor))

```

According to this output the most common Skin.color is **green**.

### 5)Find out the mean and standard deviation of height and weight. Find the tallest and shortest heroes.

```{r}


mean_and_sd <- mydata %>%
  #select(Height,Weight) %>%
  filter(Weight >0 & Height >0) %>%
  
  summarise("Mean Weight" =  mean(Weight,na.rm = TRUE),
            " Mean Height" =mean(Height, na.rm = TRUE),
            "Standart_Devition_Weight" =sd(Weight,na.rm = TRUE),
            "Standart_Devition_Height" =sd(Height,na.rm = TRUE)
           )

            
  
mean_and_sd


```
```{r, message=FALSE}

tallest_hero <- mydata %>%
 group_by(Height,name) %>%
  select(Height,name)%>%
  summarise("Height" = min(Height, na.rm = TRUE))
  
  

tail(tallest_hero)
       


```
In this table show us the tallest hero is **Fing Fang Foom**  


```{r}
shortest_hero <- mydata %>%
 group_by(Height,name) %>%
  select(Height,name)%>%
  filter(Height >0)%>%
  summarise("Height" = min(Height, na.rm = TRUE))
  
  

head(shortest_hero)

```
In this table show us the shortest hero is **Utgard-Loki**.

### 6)Create tibbles showing weight and height for good and bad Marvel heros. Compare their mean and standard
deviation weight and height.
```{r}
#weight and height for good Marvel
  good_marvel <- mydata %>% 
  select(Weight,Height,Alignment) %>% 
  filter(Alignment=="good")  %>%
  # as_tibble() turns an existing object
  as_tibble(mydata)

good_marvel

```


```{r}
#weight and height for bad Marvel
  bad_marvel <- mydata %>% 
  select(Weight,Height,Alignment) %>% 
  filter(Alignment=="bad")  %>%
  # as_tibble() turns an existing object
  as_tibble(mydata)

bad_marvel

```




```{r}
# Compare their standard


diff_marvels <- mydata %>%
  select(Weight,Height,Alignment) %>%
  summarise("sd_height_bad_marvels" = sd(Height[Alignment == "bad"],  na.rm = TRUE), 
            "sd_height_good_marvels" = sd(Height[Alignment == "good"],  na.rm = TRUE),
            "dff_sd_height_result" = ( sd_height_good_marvels - sd_height_bad_marvels),
            "sd_weight_bad_marvels" = sd(Weight[Alignment == "bad"],  na.rm = TRUE), 
            "sd_weight_good_marvels" = sd(Weight[Alignment == "good"],  na.rm = TRUE),
            "dff_sd_weight_result" = ( sd_weight_bad_marvels - sd_weight_good_marvels))
diff_marvels
```


```{r}
# Compare their mean

diff_marvels <- mydata %>%
  select(Weight,Height,Alignment) %>%
  summarise("mean_height_bad_marvels" = mean(Height[Alignment == "bad"],  na.rm = TRUE), 
            "mean_height_good_marvels" = mean(Height[Alignment == "good"],  na.rm = TRUE),
            "dff_mean_height_result" = ( mean_height_good_marvels - mean_height_bad_marvels),
            "mean_weight_bad_marvels" = mean(Weight[Alignment == "bad"],  na.rm = TRUE), 
            "mean_weight_good_marvels" = mean(Weight[Alignment == "good"],  na.rm = TRUE),
            "dff_mean_weight_result" = ( mean_weight_bad_marvels - mean_weight_good_marvels))

diff_marvels
```
### 7) Import “super_hero_powers” dataset from https://www.kaggle.com/claudiodavi/superhero-setCombine powers and
information datasets. Give 10 point to each power that is TRUE. Compute the power of each superhero. Write a dplyr
chain to plot power of female human heros and show differences for alignment. 

```{r}
super_hero_power = read.csv("C:/Users/asus/Desktop/4.Sınıf/DataScience/sumeyra_ozugur_HW1/super_hero_powers.csv") 
#super_hero_power

hero_stats <- inner_join(mydata,super_hero_power, c("name"= "hero_names"))





```

```{r}
#
super_hero_cal <- function(x) {
  
  super_power_list <- c()
  for(i in 1:660) {
    power = 0
    for (j in 12:178) {
      if(x[i, j] == "True") {
        power = power + 10
      }
      else{
        power= power
      }
      
      
    }
    super_power_list <- c(super_power_list, power)
  }
  
  #hero_stats$Power <- super_power_list
  return(super_power_list)
}



```



```{r}
hero_stats$power <- super_hero_cal(hero_stats)
```


```{r}

human_female <- hero_stats %>%
filter(Gender=="Female" & Race =="Human" & Alignment != "-" ) 



```


```{r}
#install.packages("ggplot2")
library(ggplot2)
ggplot(human_female) + geom_count(aes(x = Alignment, y = power), color = "steelblue") +
  labs(tag = "for Female Humans",
        title = "Power Scores for Alignments")

```





if Alignment  is "good" ,there are more female.
if Alignment is "neutral", there is the least female.
Alignment of the most powerful is bad.

























